Continuous gravitational waves in the lab: recovering audio signals with a table-top~optical microphone

### 2021-08-03 paper/responseRound2/AJPResponseLetter.tex

We have also made changes based on the annotated PDF from you and below answer the annotations where clarifications, etc. were needed.

Thank you again for the feedback.

Best wishes, \\
Hannah (for the co-authors)

\begin{itemize}
\item p.3, left column: Is this 1/f noise attributable to ...?
\begin{itemize}
\item The origin of this noise is uncertain. We have extended this sentence to clarify. 
\end{itemize}

\item p.4, (Figure 4 comments):  I think it is obvious that a single FT of a frequency-varying signal cannot capture the signal, so I don't see the need for Figure 4. 
\begin{itemize}
\item We are happy to remove figure 4. We added it only after the initial review in response to one of the suggestions to add a comparison of what would be detected without using Viterbi. We agree, however, that it does not add much to the explanation. We have kept a shortened version of the highlighted text to explain why we cannot use the Fourier transform in this case and we have removed the figure. 
\end{itemize}

\item p.4, Section IV A: I appreciate your desire to be all-inclusive, but is the highlighted text necessary? It is not directly related to the topic of your paper. 
\begin{itemize}
\item This expanded literature review was one of the requests from Referee 3. We agree that they are tangentially related to the work presented, so we have instead moved them to the Further Reading section in the Supplementary Material. 
\end{itemize}

\item p.5, Figure 5: This won't show up in B/W. How about indicating the probability by different sizes of the circles? 
\begin{itemize}
\item We found it very difficult to make a tidy figure using different sized circles. Instead, we now use a grey colour scheme, which looks clear and should be fine in black and white print. 
\end{itemize}

### 2021-08-03 paper/ifo-singleTone.tex
picking up two comments that were missed

\begin{figure}
	\includegraphics[width=.5\textwidth]{figures/webcam_spectrum_expt_4_0209.pdf}
	\caption{\label{fig:webcam_spectrum}
Recovery of a tone at a constant frequency: the Fourier amplitude of the intensity pattern against frequency.
The injected signal has a frequency of $2.09\,{\rm Hz}$, while the recovered signal peaks at $2.099\,{\rm Hz}$ and has an FWHM of $0.033\,{\rm Hz}$.
The plot also shows two harmonics at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ with amplitudes $10.3 \%$ and $9.8 \%$ of the amplitude of the primary peak, respectively.
}	
\end{figure}

@@

A tone with a frequency of $2.09\,{\rm Hz}$ is played through the speaker for one minute. 
The amplitude of the Fourier transform of the recovered signal is shown in Fig.~\ref{fig:webcam_spectrum}. The Discrete Fourier transform is calculated using the NumPy package for Python (see Appendix~\ref{app:code}).
We measured a peak amplitude at $2.099\,{\rm Hz}$ with a full width half maximum (FWHM) of $0.033\,{\rm Hz}$.
Two harmonics can also be seen at integer multiples of the peak frequency. 
The peaks at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ have amplitudes of $0.103$ and $0.098$ as a fraction of the height of the main peak, respectively. They are likely due to the nonlinear response of the system discussed in Section~\ref{sec:ifo}.
Also, note that the noise appears to rise at lower frequencies.

>>>>

\begin{figure}
	\includegraphics[width=.5\textwidth]{figures/webcam_spectrum_expt_4_0209.pdf}
	\caption{\label{fig:webcam_spectrum}
Recovery of a tone at a constant frequency: Here, we plot the Fourier amplitude of the intensity pattern against frequency.
The injected signal has a frequency of $2.09\,{\rm Hz}$, while the recovered signal peaks at $2.099\,{\rm Hz}$ and has an FWHM of $0.033\,{\rm Hz}$.
The plot also shows two harmonics at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ with amplitudes $10.3 \%$ and $9.8 \%$ of the amplitude of the primary peak, respectively.
}	
\end{figure}

@@

A tone with a frequency of $2.09\,{\rm Hz}$ is played through the speaker for one minute. 
The amplitude of the Fourier transform of the recovered signal is shown in Fig.~\ref{fig:webcam_spectrum}. The Discrete Fourier transform is calculated using the NumPy package for Python (see Appendix~\ref{app:code}).
We measured a peak amplitude at $2.099\,{\rm Hz}$ with a full width half maximum (FWHM) of $0.033\,{\rm Hz}$.
Two harmonics can also be seen at integer multiples of the peak frequency. 
The peaks at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ have amplitudes of $0.103$ and $0.098$ as a fraction of the height of the main peak, respectively. They are likely due to the nonlinear response of the system discussed in Section~\ref{sec:ifo}.
Also, note that the noise appears to rise at lower frequencies, however the origin of this noise is not known.
